---
title: "hex_creator"
---

In this notebook I create a hex sticker for package {isdas}. It needs that the package is installed to load some data:
```{r}
if(!require(isdas)){
  remotes::install_github("paezha/isdas")
  library(isdas)
}
```

Load packages:
```{r message=FALSE, warning=FALSE}
library(deldir)
library(gganimate)
library(ghibli)
library(hexbin)
library(spdep)
library(tidyverse)
```

Load and convert Walker Lake data to simple features:
```{r}
data("Walker_Lake")
# Function `st_as_sf()` takes a foreign object (foreign to the `sf` package) and converts it into a simple features object. If the foreign object is points, the coordinates can be named by means of the argument `coords`. 
Walker_Lake.sf <- Walker_Lake %>% 
  st_as_sf(coords = c("X", "Y"))
```

Define a bounding box to extract a subset of points:
```{r}
# Function `st_polygon()` creates an `sf` object with a polygon or polygons. In this case, we create a single polygon, a rectangle with corners given by the coordinates in the function. 
W.bbox <- st_polygon(list(rbind(c(150, 190),c(180, 190),c(180, 220), c(150, 220),c(150, 190))))
```

Extract subset of points using the bounding box:
```{r}
Walker_Lake.sf <- Walker_Lake.sf[W.bbox,]
```

Once I have an `sf` object of the points, the geometry can be used to create the Voronoi polygons:
```{r}
vpolygons <- do.call(c, st_geometry(Walker_Lake.sf)) %>% 
  st_voronoi() %>% 
  st_collection_extract()
```

Obtain the geometry of the polygons:
```{r}
Walker_Lake.v <- Walker_Lake.sf
Walker_Lake.v$geometry <- vpolygons[unlist(st_intersects(Walker_Lake.sf, vpolygons))] 
```

The intersection of the polygons with the box clips the polygons:
```{r warning=FALSE}
Walker_Lake.v <- Walker_Lake.v %>%
  st_intersection(W.bbox)
```

Plot the polygons:
```{r}
ggplot() + 
  geom_sf(data = Walker_Lake.v, 
          aes(fill = V), 
          color = NA)
```

Now create a hexagon for the sticker:
```{r}
coords_hex <- hexcoords(dx = (st_bbox(Walker_Lake.v)[["xmax"]] - st_bbox(Walker_Lake.v)[["xmin"]])/2.3,
                        dy = (st_bbox(Walker_Lake.v)[["ymax"]] - st_bbox(Walker_Lake.v)[["ymin"]])/4)

corners <- tibble(x = coords_hex$x + st_bbox(Walker_Lake.v)[["xmin"]] + (st_bbox(Walker_Lake.v)[["xmax"]] - st_bbox(Walker_Lake.v)[["xmin"]])/2,
                  y = coords_hex$y + st_bbox(Walker_Lake.v)[["ymin"]] + (st_bbox(Walker_Lake.v)[["ymax"]] - st_bbox(Walker_Lake.v)[["ymin"]])/2)

corners <- rbind(corners, corners[1,])

hexagon_1 <- st_polygon(list(as.matrix(corners))) 
hexagon_2 <- hexagon_1 %>%
  st_buffer(dist = -1.3)

hexagon <- st_difference(hexagon_1, 
                         hexagon_2)

hexagon <- st_sfc(hexagon)
```

Plot the hexagon:
```{r}
ggplot() +
  geom_sf(data = Walker_Lake.v) +
  geom_sf(data = hexagon, 
          size = 1,
          fill = NA) +
  geom_sf(data = hexagon, 
          size = 1,
          fill = "white",
          color = "red")
```

Create a mask to cover the area outside the hexagon:
```{r}
mask <- st_difference(W.bbox %>% 
                        st_buffer(dist = 1),
                      hexagon_2)

mask <- st_sfc(mask)
```

Use the original points and create buffers of different sizes. Save the results for each buffer size in a slice of table labelled by `t`. Each of these slices will become a frame in the subsequent animation:
```{r warning=FALSE}

Walker_Lake.c <- data.frame()

buf <- c(1, 2, 4, 6, 8, 10, 12, 14, 25)#seq(1, 25, 4)

for(t in 1:length(buf)){
  Walker_Lake.b <- Walker_Lake.sf %>% 
    st_buffer(dist = buf[t])
  
  Walker_Lake.j <- data_frame()
  
  for(i in 1:nrow(Walker_Lake.b)){
    Walker_Lake.j <- rbind(Walker_Lake.j,  
                           st_intersection(Walker_Lake.b[i,],
                                           Walker_Lake.v$geometry[i]))
  }
  Walker_Lake.j$t <- as.character(t)
  Walker_Lake.c <- rbind(Walker_Lake.c, Walker_Lake.j)
}

mask <- st_sf(data.frame(t = 1:length(buf),
                         geom = rep(mask, 
                                    length(buf))))

hexagon <- st_sf(data.frame(t = 1:length(buf), 
                            geom = rep(hexagon,
                                       length(buf))))
```

Example of plot with polygons and buffers at t = 2:
```{r}
ggplot() + 
  geom_sf(data = Walker_Lake.c %>% 
            filter(t == "2"), 
          aes(fill = V), 
          color = NA) + 
  geom_sf(data = Walker_Lake.v, 
          fill = NA)  +
  geom_text(aes(x = 158.5, y = 205.5), 
            label = "My text",
            size = 9) +
  geom_sf(data = mask, 
          fill = "white",
          color = NA) +
  geom_sf(data = hexagon,
          fill = "red",
          color = "red") +
  theme_void() +
  theme(legend.position = "none") 
```
Use {gganimate} to create the animation. In this animation I use the mononoke color palette from the {ghibli} package:
```{r}
anim <- ggplot() + 
  geom_sf(data = Walker_Lake.c,
          aes(fill = V),
          color = NA) + 
  geom_sf(data = Walker_Lake.v,
          size = 1,
          fill = NA,
          color = "#278B9AFF") +
  geom_text(aes(x = 158.5, y = 206.5), 
            label = "isdas",
            fontface = "bold",
            size = 12,
            color = "white") +
  geom_sf(data = mask,
          fill = "white",
          color = NA) +
  geom_sf(data = hexagon, 
          size = 0.5,
          fill = "#278B9AFF",
          color = NA) +
    
  scale_fill_ghibli_c("MononokeLight", 
                      direction = -1) +
  theme_void() +
  theme(legend.position = "none")  +
  transition_states(t,
                    transition_length = 100,
                    state_length = 1.0,
                    wrap = FALSE) +
  ease_aes()

animate(anim, 
        nframes = 200,
        start_pause = 20,
        end_pause = 20)
```

Save the animation as a gif:
```{r}
anim_save("isdas.gif",
          animation = anim)
```
